### 2023-03-23 definitions.tex
details

\section{Uniform resilience for WSTS}

@@

We add a third problem that decides whether there exists an $k$ such  that the system is $k$-resilient.
%
\problemx{bounded resilience problem (UBRP)}
{A transition system $\mathscr{S}=(S,\rightarrow)$ and two sets $Safe, Bad \subseteq S$.}
%{$\exists k \geq 0 ~ \forall s' \in D ~ s \rightarrow^* s' \implies \exists s'' \in U ~ s' \rightarrow^{\leq k} s''$ ?\newline}
{$\exists k \geq 0$ such that $\mathscr{S}$ is uniformely $k$-resilient ?\newline}

@@

\begin{proposition}\label{general}
$\mathscr{S}=(S,\rightarrow,\leq)$ is uniformely (bad,Safe)-resilient iff $bad \subseteq \pred^*(Safe)$.\\
$\mathscr{S}=(S,\rightarrow,\leq)$ is uniformely (bad,Safe)-bounded-resilient iff $\mathscr{S}=(S,\rightarrow,\leq)$ is uniformely (bad,Safe)-resilient.\\
$\mathscr{S}=(S,\rightarrow,\leq)$ is uniformely (bad,Safe)-$k$-resilient iff $bad \subseteq \pred^k(Safe)$.
\end{proposition}

@@

\subsection{Case: $Safe=\uparrow Safe$.}

\begin{theorem}\label{up-down}
The three uniform resilience problems are decidable for WSTS with effective predbasis and $Safe=\uparrow Safe$.
%	and bad is upward closed or downward closed.
\end{theorem}

\begin{proof}
Let us first solve if $\mathscr{S}=(S,\rightarrow,\leq)$ is uniformely (bad,Safe)-resilient. Since $Safe=\uparrow Safe$, and WSTS, $\pred^*(Safe)=\uparrow \pred^*(Safe)$, so $\pred^*(Safe)$ admits a finite basis $B_{\pred^*(Safe)}$. since WSTS  with effective predbasis, we may compute a finite basis of $\pred^*(Safe)$ with the backward coverability algorithm. 
%Then if bad is upward closed or downward closed, we may decide the inclusion $Bad \subseteq \uparrow B_{\pred^*(Safe)}$ which remais to compare, in both cases, two finite sets. 
if bad  is upward closed, $bad = \uparrow B_{bad}$ and $ \uparrow B_{bad} \subseteq \uparrow B_{\pred^*(Safe)}$ iff for every $b \in B_{bad}$, there is a $s \in B_{\pred^*(Safe)}$ such that $s \leq b$. similar reasonning for the other case.
hence the two uniform resilience problems are decidable.

Let us examine the uniform $k$-resilience problem (UkRP). we may compute the least $n$ such that $bad \subseteq \uparrow \pred^n(Safe)=  \uparrow \pred^*(Safe)$. S is uniformely $k$-resilient iff $n \leq k$ \alain{hum...mais il peut y avoir des chemins plus courts}and then UkRP is decidable.
\end{proof}

>>>>

@@

We add a third problem that decides whether there exists an $k$ such  that the system is $k$-resilient.
%
\problemx{bounded resilience problem (UBRP)}
{A transition system $\mathscr{S}=(S,\rightarrow)$ and two sets $Safe, Bad \subseteq S$.}
%{$\exists k \geq 0 ~ \forall s' \in D ~ s \rightarrow^* s' \implies \exists s'' \in U ~ s' \rightarrow^{\leq k} s''$ ?\newline}
{$\exists k \geq 0$ such that $\mathscr{S}$ is $k$-resilient ?\newline}

@@

\begin{proposition}\label{general}
$\mathscr{S}=(S,\rightarrow,\leq)$ is (bad,Safe)-resilient iff $bad \subseteq \pred^*(Safe)$.\\
$\mathscr{S}=(S,\rightarrow,\leq)$ is (bad,Safe)-bounded-resilient iff $\mathscr{S}=(S,\rightarrow,\leq)$ is (bad,Safe)-resilient.\\
$\mathscr{S}=(S,\rightarrow,\leq)$ is  (bad,Safe)-$k$-resilient iff $bad \subseteq \pred^k(Safe)$.
\end{proposition}

@@

\subsection{Case: $Safe=\uparrow Safe$ and $Bad=\uparrow Bad$.}

\begin{theorem}\label{up-down}
The three resilience problems are decidable for WSTS with effective predbasis and $Safe=\uparrow Safe$.
%	and bad is upward closed or downward closed.
\end{theorem}

\begin{proof}
Let us first solve if $\mathscr{S}=(S,\rightarrow,\leq)$ is (bad,Safe)-resilient. Since $Safe=\uparrow Safe$, and WSTS, $\pred^*(Safe)=\uparrow \pred^*(Safe)$, so $\pred^*(Safe)$ admits a finite basis $B_{\pred^*(Safe)}$. since WSTS  with effective predbasis, we may compute a finite basis of $\pred^*(Safe)$ with the backward coverability algorithm. 
%Then if bad is upward closed or downward closed, we may decide the inclusion $Bad \subseteq \uparrow B_{\pred^*(Safe)}$ which remais to compare, in both cases, two finite sets. 
if bad  is upward closed, $bad = \uparrow B_{bad}$ and $ \uparrow B_{bad} \subseteq \uparrow B_{\pred^*(Safe)}$ iff for every $b \in B_{bad}$, there is a $s \in B_{\pred^*(Safe)}$ such that $s \leq b$. similar reasonning for the other case.
hence the two resilience problems are decidable.

Let us examine the $k$-resilience problem (UkRP). we may compute the least $n$ such that $bad \subseteq \uparrow \pred^n(Safe)=  \uparrow \pred^*(Safe)$. S is $k$-resilient iff $n \leq k$ \alain{hum...mais il peut y avoir des chemins plus courts}and then UkRP is decidable.
\end{proof}
